The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-27 EducProposal.Rmd
Revised README and made small edits missed in the previous commit
Final edits to proposal
Reviewed pull req and knit new pdf and html

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: html_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

@@

Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz [@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts. More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be important on the way.

@@

Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: pdf_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

@@

Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts. More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be important on the way.

@@
